COVID-19 Impacted Bullying Search Intensity, Asian Population Did Not

### 2023-02-22 Outputs/Paper/paper.qmd
Update paper.qmd

Google's reported data doesn't consider the sample of users or data points such as gender, race or age. There is an evident sampling bias that occurs in this study which means the general population may be under or overrepresented, which makes it challenging because the broad population must be represented and used in our data anaylsis. User behavior is measured by how many hits particular buzzword use which can be flawed when students search using other buzzwords or not choose to use the internet to gather research on bullying or how to receive help. Google may only report positive trends and ignore negative ones leaving the data skewed.

When using the internet, the average individual is revealing information about their personal life, health, and other sensitive topics they may wish to keep private. When choosing data to report on, Google must carefully protect personal information and ensure the human right to privacy. In addition, there needs to be greater awareness and up to date information for public consumption so individuals can protect themselves.  The average user must be informed on what data is collected and how it will be used and reported on. Hackers are constantly trying to steal and use innocent users' information for their gain. Security measures must to be implemented to protect search data from unauthorized access. Our dataset needs to be looked at through this ethical lens in order to prevent discriminatory practices or breech of an individuals right to privacy.

>>>>

Google's reported data doesn't consider the sample of users or data points such as gender, race or age. There is an evident sampling bias that occurs in this study which means the general population may be under or overrepresented, which makes it challenging because the broad population must be represented and used in our data analysis. User behavior is measured by how many hits particular buzzword use which can be flawed when students search using other buzzwords or not choose to use the internet to gather research on bullying or how to receive help. Google may only report positive trends and ignore negative ones leaving the data skewed.

When using the internet, the average individual is revealing information about their personal life, health, and other sensitive topics they may wish to keep private. When choosing data to report on, Google must carefully protect personal information and ensure the human right to privacy. In addition, there needs to be greater awareness and up to date information for public consumption so individuals can protect themselves.  The average user must be informed on what data is collected and how it will be used and reported on. Hackers are constantly trying to steal and use innocent users' information for their gain. Security measures must to be implemented to protect search data from unauthorized access. Our dataset needs to be looked at through this ethical lens in order to prevent discriminatory practices or a breach of an individuals right to privacy.
